|

### 2021-08-13 02-Chp-Systematic-Review-Tools.Rmd
End of day:

In addition to being used to search systematically search health-related preprint servers, as illustrated in the systematic review presented in Chapter \@ref(sys-rev-heading), `medrxivr` has other uses. For example, I led a descriptive analysis of the change data availability statements between preprinted and published versions of the same manuscript, stratified by journal data sharing policy access, underpinned by preprint meta-data provided by `medrixvr`.

We found <!-- TODO complete -->

This study has since been published in PLOS One, and a copy is included in Appendix \@ref() .

>>>>

In addition to being used to search systematically search health-related preprint servers, as illustrated in the systematic review presented in Chapter \@ref(sys-rev-heading), `medrxivr` has other uses. For example, I led a descriptive analysis of the change in data availability statements between preprinted and published versions of the same manuscript, stratified by journal data sharing policy access, underpinned by preprint meta-data provided by `medrixvr`.

medRxiv requires that authors complete a data availability statement, but do not police

We found some evidence that data availability statements more frequently described open data on publication when the journal mandated data sharing compared to when the journal did not mandate data sharing.

This study has since been published in PLOS One, and a copy is included in Appendix \@ref(published-papers).

### 2021-08-13 03-Chp-Systematic-Review.Rmd
End of day:

---
bibliography: bibliography/references.bib
csl: bibliography/nature.csl
output:
  bookdown::word_document2: 
      toc: false
      toc_depth: 3
      reference_docx: templates/word-styles-reference-01.docx
      number_sections: false 
  bookdown::pdf_document2:
    template: templates/brief_template.tex
  bookdown::html_document2: default
documentclass: book
---
```{block type='savequote', include=knitr::is_latex_output(),quote_author='(ref:sys-rev-quote)', echo = FALSE}
"It is surely a great criticism of our profession that we have not organised a critical summary by speciality or sub-speciality, up-dated periodically, of all relevant RCTS."  
```

@@

Following ful-text screening, 127 studies met the criteria for inclusion in the review. Table \@ref(tab:studyCharacteristics-table) presents a summary of the characteristics of each study.

@@

<!-- IDEA Could include a second evidence synthesis map here to summarise Table 1, highlighting the lack of vascular dementia outcomes and the massive amount of observational data -->

@@

@@

<!-- TODO ### Risk of bias {#risk-of-bias-subheading} -->

<!-- &nbsp; -->

@@

@@

<!-- TODO Include figure here showing growth of preprint database size, and cite studies detailing increasing acceptance as a valid form of evidence.  -->

@@

>>>>

---
bibliography: bibliography/references.bib
csl: bibliography/nature.csl
output:
  bookdown::pdf_document2:
    template: templates/brief_template.tex
  bookdown::word_document2: 
      toc: false
      toc_depth: 3
      reference_docx: templates/word-styles-reference-01.docx
      number_sections: false 
  bookdown::html_document2: default
documentclass: book
---
```{block type='savequote', include=knitr::is_latex_output(),quote_author='(ref:sys-rev-quote)', echo = FALSE}
"It is surely a great criticism of our profession that we have not organised a critical summary by speciality or sub-speciality, up-dated periodically, of all relevant RCTS."  
```

@@

Following full-text screening, __XXXX__ studies met the criteria for inclusion in the review. Table \@ref(tab:studyCharacteristics-table) presents a summary of the characteristics of each study.

@@

The majority of studies were non-randomised, with only one included randomised controlled trials (the Heart Protection Study) and a relative small number of Mendelian randomisation studies. Of the non-randomised studies, many were assessments of the relationship with statis use.

Of the studies examining lipid levels, by far the most common fraction assessed was total cholesterol. The association with triglycerides levels was not consider in many papers.
<!-- TODO Check this is actually true-->

The vast majority of studies examined either all-cause dementia or Alzheimer's disease, with only a small proportion examining vascular dementia.

Many studies using electronic health records as their data source did not accurately report the diagnostic criteria used to identify cases, and of those that did, none sought to validate the accuracy of their defined code lists.

<!-- TODO Check this, and do I actually want to say this, as I don't validate my codelist in the CPRD analysis? -->

Many of the studies were conducted in electronic health record databases, which have a number of advantages over smaller more traditional cohort studies.

@@

<!-- TODO Also need to extract the codes used in each study -->

@@

### Risk of bias {#risk-of-bias-subheading}

Many of the included studies were at high-risk of bias.

The one randomised controllled trial was deemed to be a low risk of bias,

@@

The distribution of evidence between analytical designs is to be expected. Randomised controlled trials of dementia are particularly challenging, as the long follow-up, necessary due to the long latent period of the condition, makes trials logistically challenging and financial expensive. Similarly, Mendelian randomisation is a relatively new study design, and so only appears in the literature in recent years, driven by the growth of dementia GWASs (Figure \@ref(fig:typeByYear)).

<!----------------------------------------------------------------------------->
(ref:typeByYear-cap) __Study designs by year of publication__ -

(ref:typeByYear-scap) Study designs by year of publication

```{r typeByYear, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:typeByYear-cap)', out.width='100%', fig.scap='(ref:typeByYear-scap)'}
knitr::include_graphics(file.path("figures/sys-rev/type_by_year.png"))
```
<!----------------------------------------------------------------------------->

@@

<!----------------------------------------------------------------------------->
```{r preprintGrowthSetup, include=FALSE}
```

(ref:preprintGrowth-cap) __Growth of preprint repositories over time__ - Given the relative sizes of the preprint repositories at the time the searches for this review were conducted (bioRxiv n= `r n_at_search["bio"]`, medRxiv n = `r n_at_search["med"]`), the relative number of hits returned by each is expected.

(ref:preprintGrowth-scap) Growth of preprint repositories over time

```{r preprintGrowth, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:preprintGrowth-cap)', out.width='100%', fig.scap='(ref:preprintGrowth-scap)'}
knitr::include_graphics(file.path("figures/sys-rev/preprint_growth.png"))
```
<!----------------------------------------------------------------------------->
<!-- TODO Include figure here showing growth of preprint database size, and cite studies detailing increasing acceptance as a valid form of evidence.  -->

@@

One particular limitiation with regards to the risk of bias assessment is the fact that the ROBINS-E assessments were performed without the tool being finalised. This meant that there were no signalling questions to guide the domain-level risk of bias assessment, which may have influenced the accuracy with which domain-level judgements were assigned. However, there is no published empirical evidence supporting the need for signalling questions, and assessment of inter-rater reliability across the different tools did not indicate a specific problem with the ROBINS-E assessments. In fact, low agreement was common across the tools, though this is expected based on the available literature. <!-- TODO CITATION NEEDED -->

One further limitation is the fact that the risk of bias due to missing evidence assessment, combined with some empirical evidence that some studies were missed by the search but contained relevant studies is a definite limitation of this review (see Section \@Ref(rev-discussion-MR) above for a fuller discussion of this issue with respect to Mendelian randomisations studies). Unfortunately, this is probably a common limitation across all reviews, based on the way in which increased sensitivity must be balanced with a reasonable workload.

### 2021-08-13 04-Chp-CPRD-Analysis.Rmd
End of day:

@@

#### Comparing codelists

@@

@@

>>>>

<!-- TODO The rates shown are per days at risk not years-->

Crude rate ratios were calculated for each outcome and class of interest and are presented in Table \@ref(tab: )

@@

#### Comparing codelists {#comparing-codelists}

@@

<!-- TODO Check comments from co-authors have been addressed for this chapter?  -->

@@

<!-- IDEA Could include some text here about how you are more likely to get an accurate result when looking at off-target effects -->

### 2021-08-13 05-Chp-IPD-Analysis.Rmd
End of day
End of day:

@@

@@

@@

### Epic Norfolk

@@

>>>>

<!----------------------------------------------------------------------------->
&nbsp;

<!----------------------------------------------------------------------------->
&nbsp;

@@

<!----------------------------------------------------------------------------->
&nbsp;

@@

As part

@@

<!----------------------------------------------------------------------------->
&nbsp;

#### Epic Norfolk

@@

#### BRACE

#### CaPS

#### ELSA

#### EPIC Norfolk

#### Generation Scotland

#### Memento

#### NICOLA

#### TRACK HD

#### Whitehall II

_The Whitehall II study is a prospective cohort study of 10 308 participants (70% men), aged 35–55 years and recruited between 1985 and 1989 from 20 London-based Civil service departments (https://www.ucl.ac.uk/whitehallII). Clinical examinations have been performed in 1991-1994, 1997-1999, 2002-2004, 2007-2009, 2012-2013, 2015-2016 with the data from circulating metabolomic traits and cognitive testing for the present study obtained from the 1997-1999 clinic phase._ - taken from EN ID: 2140

included in previous IPD meta-analysis (Endnote ID: 2140)
